Effectful Semantics for Substructural SSA

### 2023-11-17 pldi24/paper.tex
Pulled grammar to appendix

The grammar for our syntax is given in Figure \ref{fig:ssa-grammar}, while the
typing judgements themselves are given in \ref{fig:ssa-judgements}. We begin by
giving a grammar for \textit{types} \(A, B, C\), parametrized by a set of
\textit{base types} \(X\); all syntactically well-formed types are also
semantically valid. We postulate the existence of a \textit{unit type}
\(\mb{1}\), a \textit{boolean type} \(\mb{2}\), and all tensor products \(A
\otimes B\); we write \(\otimes\) to underscore the fact that types are allowed
to be substructural, assigning every type a linearity \(\ms{lin}(A)\) satisfying
the constraints in Figure \ref{fig:ssa-structural}. In particular, the rules
\rle{unit-lin} and \rle{bool-lin} state that both the unit and boolean types
must be intuitionistic; the rule \rle{pair-lin} says that the linearity of a
pair is simply the intersection of the linearity of its components. The rules
\rle{nil-lin} and \rle{cons-lin} together say that the linearity of a context is
the intersection of the linearity of its variables, where the linearity of a
variable is the intersection of the linearity of its type and its quantity
annotation.

>>>>

The formal grammar for our syntax is given in Figure \ref{fig:ssa-grammar} in
the appendix, while the typing judgements themselves are given in
\ref{fig:ssa-judgements}. We begin by giving a grammar for \textit{types} \(A,
B, C\), parametrized by a set of \textit{base types} \(X\); all syntactically
well-formed types are also semantically valid. We postulate the existence of a
\textit{unit type} \(\mb{1}\), a \textit{boolean type} \(\mb{2}\), and all
tensor products \(A \otimes B\); we write \(\otimes\) to underscore the fact
that types are allowed to be substructural, assigning every type a linearity
\(\ms{lin}(A)\) satisfying the constraints in Figure \ref{fig:ssa-structural}.
In particular, the rules \rle{unit-lin} and \rle{bool-lin} state that both the
unit and boolean types must be intuitionistic; the rule \rle{pair-lin} says that
the linearity of a pair is simply the intersection of the linearity of its
components. The rules \rle{nil-lin} and \rle{cons-lin} together say that the
linearity of a context is the intersection of the linearity of its variables,
where the linearity of a variable is the intersection of the linearity of its
type and its quantity annotation.
